\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%% start the main stuff here %%%%%%%%%%%%%%%%%%%%

%\setcounter{section}{4}  % set counter so starts at 5 --> E
%\setcounter{page}{1}
\section{Biographical Information}

%%%%%%%%%%%%%%%%

\centerline{\bf\large Morten Hjorth-Jensen}


\medskip

%
\noindent
{\bf Professional Preparation:}
%
\vspace*{-8pt}

\begin{center}
\begin{tabbing}
\hbox to 1.3in{}\=\hbox to 1.0in{}\=\hbox to 2.5in{}\=%
      \hbox to 0.8in{}\=\kill
%
\hfill \it Institution \hfill\>\>\it Major/Title \>  \it Degree  %
     \> \it Date(s) \\
%
Norwegian University of Science\>\> Physics \> M.S.\ \> 1988 \\
and Technology, Trondheim, Norway\>\>  \>  \> \\
%
University of Oslo, Norway\>\> Physics \> Ph.D \> 1993 \\
%
ECT*, Trento, Italy\>\> Postdoctoral Researcher \>\>  1994-1996 \\
%
Nordita, Copenhagen, Denmark \>\> Postdoctoral Researcher \>\>   1996-1998 \\
\end{tabbing}
\end{center}

\vspace*{-15pt}
%
%
\noindent
{\bf Appointments and awards:}
\vspace*{-8pt}

\begin{center}
\begin{tabbing}
\hbox to 2.5in{}\=\hbox to 2.8 in{}\=\kill
%
\it Position  \>  \it Institution  \> \it Dates  \\
Associate Professor \> University of Oslo\> 1999-2001 \\
Professor \> University of Oslo\> 2001-present \\
Adjunct Professor \> Michigan State University/NSCL\> 2003-2011 \\
Professor \> Michigan State University/NSCL\> 2012-present \\
Principal investigator \> Center of Mathematics for Applications, University of Oslo\> 2003-2013 \\
Principal investigator \> Center for Computing in Science Education, University of Oslo\> 2016-present \\
\it Awards \>  \it   \> \it Dates  \\
University of Oslo award for excellence in teaching \> \> 2000 \\
Fellow of the American Physical Society \> \> 2007 \\
Oak Ridge National Laboratory excellence in research award \> \> 2008 \\
Outstanding referee award of the American Physical Society\> \> 2008 \\
University of Oslo award for excellence in teaching\> \> 2011 \\
NOKUT (Norwegian entity of quality assessment in higher education) \> \> 2012 \\
award for excellence in teaching for the 'Computing in Science Education' project\> \> \\
Elected member of the Norwegian Academy of Sciences and Letters\> \> 2013 \\
Elected member of the Royal Norwegian Society of Sciences and Letters \> \>  2015 \\
University of Oslo award for excellence in teaching \> \>  2015\\
for developing the Computational Physics group \> \> \\
%
%
\end{tabbing}
\end{center}


\noindent
{\bf Five Relevant Publications:}
\vspace*{-8pt}

%\begin{flushleft}
\begin{numberedlist}


\item  G. Hagen, A. Ekstr\"om, C.\ Forss\'en, G. R. Jansen, W. Nazarewicz, T. Papenbrock, K. A. Wendt, S. Bacca, N. Barnea, B. Carlsson, C. Drischler, K. Hebeler, M. Hjorth-Jensen, M. Miorelli, G. Orlandini, A. Schwenk, and J. Simonis, {\em Charge, neutron, and weak size of the atomic nucleus}, Nature Physics {\bf 12}, 186 (2016).


\item  A. Ekstr\"om, G. R. Jansen, K. A. Wendt, G. Hagen, T. Papenbrock, B. D. Carlsson, C.\ Forss\'en, M. Hjorth-Jensen, P. Navratil, W. Nazarewicz,{\em Accurate nuclear radii and binding energies from a chiral interaction}, Physical Review C {\bf 91}, 051301(R) (2015).

\item G. Hagen, T. Papenbrock, A. Ekstrom, G. Baardsen, S. Gandolfi, K. A. Wendt, M. Hjorth-Jensen, and C. Horowitz, {\em Coupled-cluster calculations of nucleonic matter}, Physical Review C {\bf 89}, 014319 (2014).


\item T. Papenbrock, G. Hagen, M. Hjorth-Jensen, and D. J. Dean, {\em Coupled-cluster computations of atomic nuclei}, Reports on Progress in Physics {\bf 77}, 096302 (2014).

\item A.~Ekstr\"om, G.\ Baardsen, C.\ Forss\'en, G.\ Hagen, M.\	Hjorth-Jensen, G.\ Jansen, R.\ Machleidt, W.\ Nazarewicz, 
 T.\ Papenbrock, J.\ Sarich, and S.\ Wild, {\em Optimized Chiral Nucleon-Nucleon Interaction at Next-to-Next-to-Leading Order}, Physical Review Letters {\bf 110}, 192502 (2013).



\end{numberedlist}
%\end{flushleft}


\noindent
{\bf Five Other Publications}
\vspace*{-8pt}

%\begin{flushleft}
\begin{numberedlist}
\item M. Hjorth-Jensen, M.~P.~Lombardo, and U.~van Kolck (Editors), {\em An Advanced Course in Computational Nuclear Physics; Bridging the Scales from Quarks to Neutron Stars}, Lecture Notes in Physics {\bf 936}, 2017

\item
K.\ Kowalski, D.~J.\ Dean, M.\ Hjorth-Jensen, T.\ Papenbrock, and
  P.\ Piecuch, {\em Coupled cluster calculations of ground and excited states of nuclei}, Physical  Review Letters {\bf 92}, 132501 (2004).

\item
D.~J.\ Dean and M.\ Hjorth-Jensen, {\em Pairing in nuclear systems: from neutron stars to finite nuclei},  Reviews of Modern Physics {\bf 75}, 607 (2003).


\item
H.\ Heiselberg and M.\ Hjorth-Jensen, {\em Phases of dense matter in neutron stars}, Physics Reports {\bf 328}, 237 (2000).

\item
M.\ Hjorth-Jensen, T.~T.\ S.\ Kuo, and E.\ Osnes, {\em Realistic effective interactions for nuclear systems}, Physics Reports {\bf 261}, 125 (1995).


\end{numberedlist}
%\end{flushleft}


\noindent
{\bf Synergistic Activities}
\vspace*{-8pt}

\begin{numberedlist}
\item With colleagues from the USA and other European countries, we started the Nuclear Talent initiative in 2010,
see \url{www.nucleartalent.org}, where the main aim is  provide an advanced
and comprehensive training to graduate students and young researchers
in low-energy nuclear theory. The network aims at developing a broad
curriculum that will provide the platform for a cutting-edge theory
for understanding nuclei and nuclear reactions.  The Nuclear Talent initiative has been highly welcomed by the Nuclear Physics community.
In the period 2012-2016 we have organized 11 advanced courses, with one more to be held in 2017. We have had almost 40 applicants per course on average. I have developed and taught two of the courses and been an organizer at two other courses, as well as being a teacher and main organizer at a course in 2017 on the nuclear shell model.

\item Since 1999
I have   established an activity in computational physics  at the 
Department of Physics at the University
of Oslo. In 2015 this activity was rewarded with the University of Oslo award on excellency in teaching. I have also started from scratch and developed several  courses on computational physics and many-body physics, courses I teach both at Michigan State University and at the University of Oslo. My research deals with various many-body methods and their computational aspects, with an emphasis on appplications to the nuclear many-body problem.


\item With colleagues at the University of Oslo, I have  
been strongly involved in revising the way we teach our  science courses by including computations in physics and mathematics course from the first semester of studies.
This project is called 'Computing in Science Education' 
and has received considerable support
from the University of Oslo and the Norwegian Ministry of research and education.   This activity was newly awarded as a Norwegian Center of Excellency in Education. The newly established Center of Computing in Science Education has also strong links with Michigan State University and Professor Danny Caballero, whom I collaborate with on similar projects. 


\end{numberedlist}

\noindent
{\bf Collaborators (2012-2017)}
On theory I collaborate
with Scott Bogner, Alex Brown, Heiko Hergert, Witek Nazarewicz, Filomena Nunes, Luke Roberts and Andrea Shindler at MSU, 
David Dean, Gaute Hagen and Thomas Papenbrock at UTK
and ORNL, Wick Haxton at Berkeley, Mihai Horoi at Central Michigan University,
Christian Forssen and Andreas Ekstr\"om at Chalmers, Sweden, Carlo Barbieri at Surrey, UK, 
Sweden, Francesco Pederiva at University of Trento, Takaharu Otsuka and Kazuo Takayanagi at Tokyo University, Japan, 
and Artur Polls at the University of Barcelona, Spain.  On Computing in Science education I collaborate with Professor Danny Caballero at Michigan State Univeristy, in addition to many colleagues at the University of Oslo.
Furthermore, I collaborate closely with many experimental groups nationally and internationally.

\medskip

\noindent
{\bf Graduate and Postdoctoral Advisors}
Eivind Osnes (University of Oslo, Norway, PhD advisor), Ben Mottelson (ECT*, postdoctoral advisor)
\medskip
\noindent
{\bf Thesis Advisor and Postgraduate-Scholar Sponsor (2012-2017)}
\noindent
{\it Graduate Advisor:} Gustav Baardsen (PhD UiO), Gustav Jansen (PhD UiO), Torquil McDonald S\o renssen (PhD UiO),
John Bower (PhD MSU), Jusin Lietz (PhD MSU), Sam Novario (PhD MSU), Fei Yuang (PhD MSU). In total in this period,
22 Master of Science students have completed their theses with me as supervisor and three studentes have completed their  PhD theses \\ {\it Postdoc
Sponsor:} Andreas Ekstr\"om (UiO and MSU), \O yvind Jensen (UiO),
Simen Kvaal (UiO), Elise Bergli (UiO), S\o lve Selst\o\ (UiO) Nicolas
Michel (MSU). Since I was hired at the University of Oslo I have supervised in total 53 Master of Science Students, 12 PhD students and six post-doctoral fellows.






